
\subsection{Model Driven Engineering}
Model-driven engineering (MDE) is a software development approach that focuses on creating and using domain-specific models as the main artifacts for software development. These models are used to represent the different aspects of the software system, such as its functionality, behavior, structure, and data. MDE aims to provide a higher level of abstraction for software development, allowing developers to focus on the problem domain rather than on the technical details of the implementation\cite{methodologyBasedMDE}..

MDE is based on the idea that models can be transformed into different representations, such as code, configuration files, or documentation. This process is supported by model transformation techniques, which are used to transform the models into the desired representations.

One of the main benefits of MDE is that it allows developers to work with domain-specific languages (DSLs). DSLs are specialized languages that are tailored to a particular problem domain. They allow developers to express the concepts and rules of the domain in a more concise and intuitive way, making it easier to understand and manipulate the models.
There are different types of DSLs, ranging from visual languages \cite{designDSLandIDEforIOTa}, such as UML diagrams, to textual languages, such as regular expressions. Each type of DSL has its own advantages and disadvantages, and the choice of a particular DSL depends on the specific needs of the project.

In addition to simplifying the development process, MDE and DSLs can also improve the quality and maintainability of the software. By using models as the main artifacts, developers can better capture the intended behavior and structure of the system\cite{MDE4IOT}, making it easier to understand and modify the software. This can reduce the number of defects and improve the overall reliability of the system.

In summary, MDE and DSLs provide a powerful toolset for software development, allowing developers to work at a higher level of abstraction and to focus on the problem domain rather than on the technical details. By using models and domain-specific languages, developers can create more reliable and maintainable software systems that are easier to understand and modify.

\subsection{Domain Specification Language: ECG et EEG}

Electrocardiograms (ECG) and Electroencephalograms (EEG) are processes that measure the heart and brain activities respectively using the electrical signals they produce. The correct modeling and treatment of these signals is essential for medical purposes because they are critical for the diagnosis and treatment of diseases. During the following sections, several applications for the treatment and modeling of these signals are going to be shown.

\subsubsection{Changes in Cortical Activity During Real and Imagined Movements: an ERP Studies}

Changes in cortical activities in movement imagination MI (when a person imagines performing a movement) and movement execution ME(when a person actually performs a movement) are similar. There is a similar topology for the activated brain areas for both ME and MI, especially in the collateral motor area of the brain. However contrary to ME, the activation of the motor neurons is insufficient for triggering spinal motor neurons, and therefore the movement is blocked.

Therefore, MI is very important for the use of prosthetic implants as it activates the motor areas of the brain even when it does not perform an action. Understanding the brain behavior during the MI is important, for this purpose electroencephalogram (EEG) is used, with the intent of recording the brain’s electrical activity and describing it through complex waves.  However, the signals are not-periodical, don't have standardized patterns, and have small voltage amplitudes, which make them easy to be mixed up with noise from exterior factors like heartbeat, muscle movements, and environment. In order to solve this, window functions are used to reduce noise and enhance movement intention signals.

\subsubsection{Window functions}

Window functions are used in signal processing for reducing noise and enhancing the original signal. There are several types of functions, each of them serving different types of signal waves.  For this reason, two studies were made to compare the performance of different window functions over EEG signals.\\

In \textit{Window Function for EEG Power Density Estimation and Its Application in SSVEP Based BCIs} the Rectangle, Hamming, Hann and Triangular functions were compared and the triangular function was the most accurate. Moreover, it was found that the use of a high pass filter enhances the accuracy of the signal produced.\\

On the other hand, in Window Functions Analysis in Filters for EEG Movement Intention Signals Bartlett, Blackman, Hanning, Hamming, Kaiser, Rectangular and Triangular window functions were compared, calculating the euclidean distance of the signal to the simulated signal. It was found that Blackman and Barlett window functions have the highest accuracy describe these signals.

\subsubsection{Formalizing electrocardiogram (ECG) signal behavior in event-B}

As the electrocardiogram is a process for measuring the heart's electrical signals, it is used for medical examinations to evaluate several medical conditions. This makes the treatment of ECG signals critical in situations like a stroke, where the medical response needs to be urgent. For this reason, its treatment needs to be done in real-time. This study implements a real-time monitoring system, using LabView, a medical laboratory toolkit, to treat the heartbeat signals by reducing noise, and when an anomaly is found an SMS is sent to a designated doctor.

\subsubsection{Development of real-time ECG signal monitoring system for telemedicine application}
There is a lack of formal specification of the interpretation of these signals. This study proposes a model in Event-B, a language for specifying and verifying complex systems using proof. The three stages in which a heartbeat produces signals depolarization were modeled, namely atrial depolarization, ventricular depolarization, and ventricular repolarization, and among them three characteristic waves observable by the ECG P, QRS and T. It was constructed using invariants of the heart behavior, which could help identify when a problem is occurring.


\subsection{Artificial Intelligence} 
Artificial intelligence has been an interesting domain in this era, allowing developers and others to benefit from its capacity. Although this domain is usually vast, its current branch called Machine Learning(ML) has seen a rise in popularity. Machine learning uses statistical modelling and computational learning technology in order to recognise pattern in a given datasets. All the ML existing techniques can be divided into several categories based on its different characteristic: frequency of learning, nature of learning, etc.

For the frequency of learning, we can divide the ML techniques into two categories, online and offline learning. Online Learning uses real time input and output to incrementally modify its state for each observation. However in an offline learning, a batch of this observations are sent to the model from time to time.

Nonetheless, ML techniques can also be recognized from its different nature of learning. In this category, the ML techniques are called supervised and unsupervised learning. A supervised learning differs from unsupervised learning in terms of the pre-recognition of the labels or classed that can be found in the datasets, such as regression or classification. The unsupervised techniques starts the learning process with zero knowledge of the data, constructing the labels in the dataset one step after another, where the clustering technique is the mostly wide used. 

The challenges in using Artificial Intelligence(or more precisely Machine Learning) in Model-Driven Engineering is due to the lack of datasets that the ML models can learn from. Even if the datasets are available, the heterogenous nature of the datasets specifically for the Internet of Things(IoT) technologies are delimiting the application of AI techniques in the domain. The learning granularity of the AI models needs to be fine-grained in order to obtain a more accurate and efficient learning.

The different notions of models in AI and MDE also brings some difficulty in integrating these two domain together. ML models or techniques as mentioned above are completely distinct than the models used in MDE; one is a statistical model while another is a structural model. Various works such as ML-Quadrat are looking forward to create a synergy between this models, allowing a more seamless model engineering in the domain.

\subsection{IoT Definition : }
%Do not forget that we are particularly working on IoT domain application and specifically on signal synchronisation for healthcare use case (EEG and ECG).
  \begin{itemize}
  
      \item IOT stands for Internet Of Things, it can be defined as " a self configuring and adaptive system consisting 
      of networks of sensors and smart objects whose purpose is to interconnect ‘all’ things" 
      according to the IEEE Iot Community\cite{buildingIot}.
      Three general classes for use cases of IOT in healthcare can be defined. They are the purposes for  
      collecting data : Tracking humans, tracking things and tracking both \cite{buildingIot}.

      \item One important aspect of Iot, especially for healthcare Iots, is clock synchronisation. 
      A solution for this challenge has been proposed in 2018 \cite{clockIot}:
      it is called SPoT, it is a packet exchange protocol, and it has advantages in comparison to other standard protocols.

      \item IOT applications\newline
      \begin{itemize}
        \item Iot in healthcare domains is widely used, so there is a need for
        formalizing the way to describe, specify and implement an IOT application \cite{buildingIot}. 
        There is also a need for an expertise in healthcare domain and         
        a strong collaboration between engineers and healthcare workers.
        \item One exemple of an Iot implementation a real-time
        electrocardiogram (ECG) acquisition application \cite{ecgIot}.
        \item Finally, the article \cite{yourOwnIot} targets anyone 
        who wants to make their own iot device by proposing a selection of           
        hardwares, platforms, and programming langages for Iot creation. 
        It compares different aspects such as prices, connectivity or compatibility.
      \end{itemize}
  \end{itemize}

\subsection{GALS \& Clock Synchronisation}

\subsubsection{Globally-asynchronous locally-synchronous systems}

Synchrounous systems are systems which "each of its components receive a common periodic signal (clock) that is used to control its operation and its interaction with other components". Synchrounous systems are not efficient when its internal components are not tied to the same clock. A solution is to blend asynchronous solutions with synchronous solutions, this is the purpose of this paper which aim to present globally-asynchronous locally-synchronous systems, introduced  as an optimum middle between synchrounous and asynchrounous systems and as a solution to implement multiclocks systems. The Chapter 2 of this paper provide background on synchronization and asynchrounous communication protocol. Chapter 3 discusses the reasons that led to the GALS approach. Chapter 4 is about the class of "unsynchronous" machines and how they are constructed. Chapter 5 is about the class of "escapement" machines and presents algorithms to verify their value-safety.


\subsubsection{The ESTEREL language}

ESTEREL is a synchrounous programming language for the developpement of reactive synchronous parralel systems. A reactive system which is continuously interacting with the exteral environnement, continously waiting from outside activation in order to react. An ESTEREL program can be viewed as a specification since it is a set of rules, each rule describe which signal is awaited and how the system will react on activation. ESTEREL programs have formal and mathemical semantics described in this paper. This paper also describe how ESTEREL is implemented.


\subsubsection{SystemJ: A GALS language for system level design}

SystemJ is a system-level programming language which can be used to implements GALS. Like ESTEREL, SystemJ also targets the synchronous reactive systems. SystemJ programs are "a collection of asynchronous nodes called clock-domains where each clock-domain is a purely synchronous node analogous to a SR program in a language like ESTEREL".

\subsubsection{Formalization and Correctness of the PALS Architectural Pattern for Distributed Real-Time Systems}

Physically Asynchronous Logically Synchronous (PALS) is a architectural pattern that targets the developpement of Distributed Real-Time Systems (DRTS), the key idea of PALS is to reduce the effort of designing, verifying and implementing DRTS. This paper presents a formal method for PALS transformation expressed in Real-Time Maude formal specification language. A bisimulation theorem "showing that the original synchronous design and
the so-called stable states of the corresponding PALS asynchronous design constitute bisimilar systems, and two further generalizations of such a theorem" and An avionics case study illustrating the usefulness of the PALS patern for formal verification purposes.
